\documentclass[resmargin,line]{res}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{color}
\usepackage[top=0.75in,bottom=0.75in,
            right=0.5in,left=0.5in]{geometry}

\textwidth=6.0in
\sectionskip=5mm

\itemsep=0in
\parsep=0in

% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 
\newcommand{\ts}{\textsuperscript}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\setlist[itemize]{noitemsep,topsep=0pt}

\begin{document}

\name{Andre Kuhlenschmidt}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
450 South Main Street      & {\it E-mail:} andre.kuhlenschmidt@gmail.com \\
Unit 803                           & {\it Phone:}  (812) 325-7906 \\
Seattle, WA, 98104          & {\it Github:} github.com/akuhlens  \\       
                                       & {\it WWW:} akuhlens.github.io \\     
\end{tabular}

\section{\sc Objective }
Computers are tools that help humans scale to the problems they are
solving. Programming languages are tools that help humans scale to the
computers they are using. I want to design and build compilers,
runtime systems, type systems, and other tools that make it easier
to produce quality software. 

\section{\sc Education}
{\bf Indiana University},
Bloomington, Indiana USA\\
\vspace*{-.15in}
\begin{list1}
\item[] {\em Ph.D. Candidate ABD}, Computer Science, Advisor: Jeremy Siek \hfill{} {\bf May 2021}
\item[] {\em M.S.}, Computer Science  \hfill {\bf May 2016}
\item[] {\em B.S.}, Business, Major: Entrepreneurship \hfill{} {\bf May 2010}
\end{list1}

%% {\bf Indiana University, Kelley School of Business}, Bloomington, Indiana USA\\
%% \vspace*{-.15in}
%% \begin{list1}

%% \end{list1}

\section{\sc Experience}

{\bf Semgrep}, Remote \\
{\em Senior Software Engineer} \hfill {\bf June 2023 -- Current}\\
%
\begin{itemize}
  \vspace*{-.3cm}
  % Balance individual effort with teamwork throughout debugging, prototyping, and productization
\item Worked with a small team to bring a security product to beta release in a single quarter.
  % Utilized security researches to identify most valuable features.
  % Ballanced tight timeline with application features,
      % 1. In the beginning we used security experts to identify the minimum feature set for a secrets scanning
      %     Found the minimal path to this feature set, while not accumulating undue technical debt,
      % 2. Once we established that feature set we incrementally evaluated what is the most impactful thing we can do in the amount of time that we have left.
% Partner with application teams to investigate interesting and meaningful compilation problems from the HPC community
\item Collaborated with customer success engineers to enable our static analysis engine to scale to customer
  codebases, address specific customer needs, and improve user experience.
\end{itemize}


{\bf Meta}, Redmond, Washington USA\\
{\em Software Engineer} \hfill {\bf December 2020 -- April 2023}\\
% Note from Annie focus on the implications of these statements and the impact that these bullets have.
\begin{itemize}
\vspace*{-.3cm}
  % Solve difficult problems at the intersection of compilers, programming models, and high-performance computing architectures  
\item Collaborated on the design of a programming language to make developing performant distributed applications easier,
  enabling developers to write applications that migrate between cloud and device to minimize power consumption.
  % Minimal device power = Distributed Application Logic and Compute in cloud
  % Making distrubuted programming accessible and transparent to the masses (common developers)
  % Build a programming language that makes it easier.
% Discuss and refine software designs and implementation strategies with peers
\item Started and led a research paper reading group to regularly review and discuss papers relevant to our compiler's design
  which improved our implementation strategies.
\item Implemented algebraic datatypes, closures, mutuable arrays, local mutable variables, and a compiler backend targeting LLVM.
\item Rated as Exceeding Excpectations for Individual Contributor Level 4 in 2022.
\end{itemize}

{\bf Indiana University}, Bloomington, Indiana USA\\
{\em Graduate Research Assistant} \hfill {\bf January 2014 -- December 2020}\\
%
\begin{itemize}
\vspace*{-.3cm}
\item Evaluated implementation techniques for sound gradually typed
  programming languages.
\item Developed an ahead-of-time compiler called Grift.
\item Measured performance improvements in compiler via benchmark experiments.
\item Designed semantics that facilitate safety and efficiency.
\end{itemize}

{\bf Meta}, Seattle, Washington USA\\
{\em Software Engineering Ph.D. Intern} \hfill {\bf May 2019 -- August 2019}\\
%
\begin{itemize}
\vspace*{-.3cm}
\item Extended Flow type checker to interactively edit code based on type inference.
\item Extended Flow to automatically fix a class of errors that are caused by omitting
  type annotations.
\end{itemize}

{\bf Indiana University}, Bloomington, Indiana USA\\
{\em Assistant Instructor} \hfill {\bf January 2016 -- May 2018}\\
{\color{white} . } \quad \hfill {\bf August 2012 -- May 2014}\\
%
\begin{itemize}
\vspace*{-.35cm}
\item Planned and constructed materials and software for
  courses in programming language semantics and implementation,
  operating systems, and embedded systems.
\item Instructed lab sessions of 5-30 students.
\item Recognized as Assistant Instructor of the Year in 2018.
\end{itemize}
%
%% Assisted in the instruction of courses teaching programming
%% language implementation, embedded programming, and operating
%% systems. Responsibilities include teaching lab sections of 5-30
%% students, creating assignments, and developing course software.

\section{\sc Skills}
{\bf Languages:} OCaml, Racket, Scala, C, Haskell, Java, Python, Coq, C++\\
{\bf Tools and Platforms:} Bash, Hg, Git, Make, Github Actions, Linux, Mac OS

\section{\sc Conference Papers}
{\bf Toward Efficient Gradual Typing for Structural Types via Coercions}
Andre Kuhlenschmidt, Deyaaeldeen Almahallawi, and Jeremy G. Siek.
In Programming Language Design and Implementation 2019.

\section{\sc Refereed \, Articles}

{\bf An Efficient Compiler for the Gradually Typed Lambda Calculus}
Andre Kuhlenschmidt, Deyaaeldeen Almahallawi, Jeremy G. Siek.
In Scheme and Functional Programming Workshop, 2018.

{\bf A Systematic Performance Evaluation of Gradually Typed Functions
  and References}.
Andre Kuhlenschmidt, Deyaaeldeen Almahallawi, Jeremy G. Siek.
In Scripts to Programs Workshop, STOP, 2016.

{\bf Towards Absolutely Efficient Gradual Typing}
Andre Kuhlenschmidt, Deyaaeldeen Almahallawi, and Jeremy G. Siek.
In Scripts to Programs Workshop, STOP, 2015.

\section{\sc Open Source Projects}

{\bf Grift}
\hfill {\bf May 2014 -- December 2021}\\
\vspace*{-.35cm}
\begin{itemize}
  %% \item An ahead-of-time compiler for comparing implementation
  %%   techniques of gradual typing.
\item Collaborator on an optimizing compiler for a gradually typed
  Lisp to native code.
\item Utilizes {\em space-efficient coercions} to enforce soundness of
  the static type system, which results in a performance increase that
  is multiple orders of magnitude.
\end{itemize}


\section{\sc Professional Activities}

IU Luddy Graduate Education Committee, Student Representative
\hfill January 2018 - August 2020\\
OOPSLA Artifact Evaluation Committee \hfill August 2018\\
SPLASH Student Research Competition Program Committee \hfill August 2018

\end{resume}
\end{document}
